@inproceedings{Mengye2023m4,
  title={M4Raw: A Multi-Contrast Multi-Repetition Multi-Channel Raw K-space Dataset for Low-Field MRI Reconstruction},
  author={Mengye Lyu and Lifeng Mei and Sixing Liu and S. Huang and Yi Li and Kexin Yang and Yilong Liu and Ed X. Wu},
  booktitle={Proc. Int. Soc. Magn. Reson. Med 31 (2023)},
  organization={International Society for Magnetic Resonance in Medicine},
  issn = {1545-4428},
  pages={404},
  year={2023}
}

@inproceedings{lifen2023ismrm,
  title={VarNet-based Simultaneous Multislice Reconstruction for Low Noise Amplification and Flexible Calibration},
  author={Lifeng Mei and Celia.M. Dong and  Sixing Liu and S. Huang and Mengye Lyu},
  booktitle={Proc. Int. Soc. Magn. Reson. Med 31 (2023)},
  issn = {1545-4428},
  organization={International Society for Magnetic Resonance in Medicine},
  pages={950},
  year={2023}
}

@inproceedings{sixin2023ismrm,
  title={Deep Learning Augmented PROPELLER Reconstruction for Improved
MRI Motion Correction},
  author={{Sixing Liu} and Lifeng Mei and Shoujin Huang and Mengye Lyu},
  booktitle={\textbf{International Society for Magnetic Resonance in Medicine (ISMRM)}},
  issn = {1545-4428},
  pages={3706},
  year={2023}
}

@incollection{mei2023space,
  title={Space-Time Deformable Attention Parallel Imaging Reconstruction for Highly Accelerated Cardiac MRI},
  author={{Lifeng Mei} and Yang, Kexin and Li, Yi and Shoujin Huang and Liu, Yilong and Lyu, Mengye},
  booktitle={\textbf{International Workshop on Statistical Atlases and Computational Models of the Heart}},
  doi = {10.1007/978-3-031-52448-6_38},
  url = {https://link.springer.com/chapter/10.1007/978-3-031-52448-6_38},
  pages={400--409},
  year={2023},
  organization={Springer}
}

@inproceedings{ruan2023predicting,
  title={Predicting Microsatellite Instability from Pathological Images Using Self-Supervised Learning Methods},
  author={Ruan, Ruyun and Huang, Shoujin and Su, Liyilei and Khan, Rashid and Huang, Bingding},
  booktitle={Proceedings of the 2023 International Conference on Advances in Artificial Intelligence and Applications},
  pages={223--228},
  year={2023}
}
